Concurrent Programming with CXL

### 2020-06-25 book/paper.tex
Latest

>>>>

\section*{Exercises}
\begin{problems}
\item A common pattern in distributed systems is the so-called \emph{client/server}
model, where a server process provides services to a set of clients.  The clients
send request messages to the server, and the server sends a response to each
request.  Develop a protocol for a single client and server using the same network
model as for the ABP protocol.  By way of example, let a request contain an
integer and the response consist of the square of that integer.
\end{problems}
